### 2024-08-21 ms.qmd
Updates

_Table 1. Estimates of the effects of each treatment and their interaction on the latency, choice, and interest shown for the higher amount of food in each of the numerical discrimination tests. The table shows the comparissons for each predictor and the p~mcmcm~ value of the comparissons. In bold, the estimates with p~mcmc~ < 0.05._

@@

    effect_temp <- format_dec(mean(c(Hot_CORT, Hot_Control)) - mean(c(Cold_CORT, Cold_Control)), 3)
    effect_hormone <- format_dec(mean(c(Hot_Control, Cold_Control)) - mean(c(Hot_CORT, Cold_CORT)), 3)
    interaction <- format_dec((mean(Hot_Control) - mean(Cold_Control)) - (mean(Hot_CORT) - mean(Cold_CORT)), 3)

@@

    pmcmc_temp <- format_p(pmcmc(c(Hot_CORT, Hot_Control) - c(Cold_CORT, Cold_Control)), 3)
    pmcmc_hormone <- format_p(pmcmc(c(Hot_Control, Cold_Control) - c(Hot_CORT, Cold_CORT)), 3)
    pmcmc_interaction <- format_p(pmcmc((Hot_Control - Cold_Control) - (Hot_CORT - Cold_CORT)), 3)

@@

# Split the table_data df by task

@@

    hline(i = c(3,6), j = c(1:7), part = "body") %>% # To make some horizontal lines
    vline(i = (1:9), j = c(2:6), part = "body") %>% # To make some vertical lines on body
    vline(i = 2, j=c(2:6), part = "header") %>% # To make some vertical lines on header
    autofit() 

@@

_Table S1.- Summary of the model_

```{r, tbl-summary}
#| label: tbl-summary
#| tbl-cap: "Summary of the model fitted to the data."
```

@@

_Table S2.- Evaluating whether choice diff from 0.5 and interest diff from 0_
```{r, tbl-summary}
#| label: tbl-summary
#| tbl-cap: "Summary of the model fitted to the data."
```

@@

_Table S3.- Number of individuals per treatment that chose the right (R) or left (L) side in each of the numerical tests. p-value indicates the result of the binomial test comparing the number of choices between sides._
```{r, tbl-sides}
#| label: tbl-sides
source(here("R", "func.R"))
#
# 1) MAKING THE DF FOR THE TABLE
data_sides <- data_num %>%
  group_by(trt, test_type) %>% # Group by treatment and test
  summarise(
    right_choices = sum(side_choice == "Right", na.rm = TRUE),
    left_choices = sum(side_choice == "Left", na.rm = TRUE),
  ) %>% # Count the number of correct choices
  rowwise() %>%  # Ensure that mutate works row by row
  mutate(
    total_choices = right_choices + left_choices,  # Calculate total choices
    p_value = format_dec(binom.test(right_choices, total_choices)$p.value, 2)  # Perform binom test
  ) %>% # Test for differences between sides
  ungroup() %>%  # Remove rowwise grouping
  mutate(choices_Right_Left_p = paste0("R = ", right_choices, " | L = ", left_choices, " , p = ", p_value), # Create a column with the choices
        trt = recode(trt, 
                 "B_23" = "CORT-Cold (n = 20)", 
                 "A_23" = "Control-Cold (n = 20)", 
                 "B_28" = "CORT-Hot (n = 20)", 
                 "A_28" = "Control-Hot (n = 20)")) %>% # To order the treatments
  dplyr::select(trt, test_type, choices_Right_Left_p) %>% # Remove unused columns
  pivot_wider(names_from = test_type, values_from = c(choices_Right_Left_p)) %>% # To split between tests
data.frame()
#
# 2) MAKING THE TABLE
#
# Split the table_data df by task
sides_table <- flextable(data_sides) %>%
  compose(j = 1, value = as_paragraph(""), part = "header") %>%
  compose(j = 2, value = as_paragraph("1 VS 4"), part = "header") %>%
  compose(j = 3, value = as_paragraph("1 VS 3"), part = "header") %>%
  compose(j = 4, value = as_paragraph("2 VS 4"), part = "header") %>%
  compose(j = 5, value = as_paragraph("2 VS 3"), part = "header") %>%
  compose(j = 6, value = as_paragraph("3 VS 4"), part = "header") %>%
  set_table_properties( width = 0.9, layout = "autofit") %>%
  align(align = "center", part = "all")
sides_table
```

@@

_Table S4. Number of individuals per treatment that chose the cricket oriente horizontally (Horizontal) or vertically (Vertical) in our control tests. p-value indicates the result of the binomial test comparing the number of choices between both choices._
```{r, tbl-orientation}
#| label: tbl-sides
source(here("R", "func.R"))
#
# 1) MAKING THE DF FOR THE TABLE
data_or_res <- data_orient %>%
  mutate(choice_or = ifelse(choice_horizontal == 0, "Vertical", "Horizontal")) %>%
  dplyr::select(trt, choice_horizontal, choice_or) %>%
  group_by(trt) %>% # Group by treatment and test
  summarize(
    Horizontal_Count = sum(choice_or == "Horizontal"),
    Vertical_Count = sum(choice_or == "Vertical")
  ) %>% # Count the number of horizontal and vertical choices
  rowwise() %>%  # Ensure that mutate works row by row
  mutate(
    total_choices = Horizontal_Count + Vertical_Count,  # Calculate total choices
    p_value = format_dec(binom.test(Horizontal_Count, total_choices)$p.value, 3)  # Perform binom test
  ) %>% # Test for differences between sides
  ungroup() %>%  # Remove rowwise grouping
  mutate(trt = recode(trt, 
            "B_23" = "CORT-Cold (n = 20)", 
            "A_23" = "Control-Cold (n = 20)", 
            "B_28" = "CORT-Hot (n = 20)", 
            "A_28" = "Control-Hot (n = 20)")) %>% # To order the treatments
  dplyr::select(trt, Horizontal_Count, Vertical_Count, p_value) %>% # Remove unused columns
data.frame()
#
# 2) MAKING THE TABLE
#
# Split the table_data df by task
orient_table <- flextable(data_or_res) %>%
  compose(j = 1, value = as_paragraph(""), part = "header") %>%
  compose(j = 2, value = as_paragraph("Horizontal"), part = "header") %>%
  compose(j = 3, value = as_paragraph("Vertical"), part = "header") %>%
  compose(j = 4, value = as_paragraph("p-value"), part = "header") %>%
  set_table_properties( width = 0.9, layout = "autofit") %>%
  align(align = "center", part = "all")
orient_table
```

>>>>

_Table 1. Estimates of the effects of temperature, CORT, and their interaction on latency, choice, and interest shown for the higher amount of food in each of the numerical discrimination tests. The table shows the comparissons for each predictor and the p~mcmcm~ value of the comparissons. In bold, the estimates with p~mcmc~ < 0.05._

@@

    effect_temp <- format_dec(mean(c(Hot_CORT, Hot_Control)) - mean(c(Cold_CORT, Cold_Control)), 2)
    effect_hormone <- format_dec(mean(c(Hot_Control, Cold_Control)) - mean(c(Hot_CORT, Cold_CORT)), 2)
    interaction <- format_dec((mean(Hot_Control) - mean(Cold_Control)) - (mean(Hot_CORT) - mean(Cold_CORT)), 2)

@@

    pmcmc_temp <- format_p(pmcmc(c(Hot_CORT, Hot_Control) - c(Cold_CORT, Cold_Control)), 2)
    pmcmc_hormone <- format_p(pmcmc(c(Hot_Control, Cold_Control) - c(Hot_CORT, Cold_CORT)), 2)
    pmcmc_interaction <- format_p(pmcmc((Hot_Control - Cold_Control) - (Hot_CORT - Cold_CORT)), 2)

@@

 font.size = 10,
 layout = "autofit")
# Create the table

@@

    hline(i = c(3,6), j = c(1:7), part = "body") # To make some horizontal lines 

@@

_Table S1.- Summary of the model fitted_

```{r, summary_org}
#| label: summary_org
#
## Get the summary of the posteriors to get the estimates of each parameter of the model
sum <- summary(posteriors)
## Extract the values of the summary
sum_df <- as.data.frame(sum) %>%
  dplyr::select(-mad) %>%
  filter(!str_detect(variable, "^r_"))
```

For loglatency
```{r, tbl-summary_lat}
#| label: tbl-summary_lat
#| tbl-cap: "Summary of the model fitted for the latency variable."
#
source(here("R", "func.R"))
## Get df only for latency
df_sum_lat <- sum_table_org(sum_df, "lat")
## Make table
table_sum_lat <- flextable(df_sum_lat)
table_sum_lat
```

For choice
```{r, tbl-summary_choice}
#| label: tbl-summary_choice
#| tbl-cap: "Summary of the model fitted for the choice variable."
#
source(here("R", "func.R"))
## Get df only for choice
df_sum_choice <- sum_table_org(sum_df, "choice")
## Make table
table_sum_choice <- flextable(df_sum_choice)
table_sum_choice
```

For compared interest
```{r, tbl-summary_int}
#| label: tbl-summary_int
#| tbl-cap: "Summary of the model fitted for the interest variable."
#
source(here("R", "func.R"))
## Get df only for interest
df_sum_int <- sum_table_org(sum_df, "int")
## Make table
table_sum_int <- flextable(df_sum_int)
table_sum_int
```

Other effects
```{r, tbl-summary_other}
#| label: tbl-summary_other
#| tbl-cap: "Summary of the model fitted for other effects."
#
source(here("R", "func.R"))
## Get df only for interest
df_sum_other <- sum_df %>%
  filter(!str_detect(variable, "^b_"))
## Make table
table_sum_other <- flextable(df_sum_other)
table_sum_other
```

@@

_Table S2.- Estimated mean probability of choosing first the higher amount (Choice) and the mean interest for the higher amount of food (Interest) per treatment group for each of the numerical tests performed. p indicates the p~mcmcm~ value (p) of testing the hypothesis Choice ≠ 0.5, and Interest ≠ 0, which would indicate a preference towards one of choices (> towards higher amounts, < towards lower amounts) of the comparissons._
```{r, tbl-disc}
#| label: tbl-disc
#| tbl-cap: "Estimated probability of choosing first the higher amount (Choice) and the interest for the higher amount of food (Interest) per treatment group for each os the tests performed. p indicates the p~mcmcm~ value of testing the hypothesis Choice ≠ 0.5, and Interest ≠ 0, which would indicate a preference towards one of choices (> towards higher amounts, < towards lower amounts) of the comparissons."
disc_list <- list()
variable <- c("Choice", "Interest")
for(c in variable){
  if(c == "Choice"){
    val <- 0.5
  } else if(c == "Interest"){
    val <- 0
  df_disc <- data.frame()
  for(d in test){
      dplyr::select(dplyr::matches(d))
    Cold_CORT <- post_mod[[paste0("X", d, "_Cold_CORT")]]
    Cold_Control <- post_mod[[paste0("X", d, "_Cold_Control")]]
    Hot_CORT <- post_mod[[paste0("X", d, "_Hot_CORT")]]
    Hot_Control <- post_mod[[paste0("X", d, "_Hot_Control")]]
    # Calculate means and pmcmc values
    Cold_CORT_mean <- format_dec(mean(Cold_CORT), 2)
    Cold_Control_mean <- format_dec(mean(Cold_Control), 2)
    Hot_CORT_mean <- format_dec(mean(Hot_CORT), 2)
    Hot_Control_mean <- format_dec(mean(Hot_Control), 2)
    pmcmc_Cold_CORT <- format_p(pmcmc(Cold_CORT, null = val), 2)
    pmcmc_Cold_Control <- format_p(pmcmc(Cold_Control, null = val), 2)
    pmcmc_Hot_CORT <- format_p(pmcmc(Hot_CORT, null = val), 2)
    pmcmc_Hot_Control <- format_p(pmcmc(Hot_Control, null = val), 2)
    treatment_names <- c("Cold-CORT", "Cold-Control", "Hot-CORT", "Hot-Control")
    values_means <- c(Cold_CORT_mean, Cold_Control_mean, Hot_CORT_mean, Hot_Control_mean)
    values_pmcmc <- c(pmcmc_Cold_CORT, pmcmc_Cold_Control, pmcmc_Hot_CORT, pmcmc_Hot_Control)
    temporal_df <- data.frame(Treatment = treatment_names,
                        Effect = values_means,
                        Test = d,
    df_disc <- rbind(df_disc, temporal_df)
  df_disc$Variable <- c
  disc_list[[c]] <- df_disc
disc_df <- do.call(rbind, disc_list)
disc_df_final <- as.data.frame(disc_df, stringsAsFactors = FALSE) %>%
  mutate(pmcmc = gsub("^= ", "", pmcmc)) %>%
  pivot_wider(names_from = Test, values_from = c(Effect, pmcmc), names_prefix = "") %>%
  dplyr::select(Variable, Treatment, 
                Effect_1VS4, pmcmc_1VS4,
                Effect_1VS3, pmcmc_1VS3,
                Effect_2VS4, pmcmc_2VS4,
                Effect_2VS3, pmcmc_2VS3,
                Effect_3VS4, pmcmc_3VS4)
# Create the table
disc_table <- flextable(disc_df_final) %>%
    add_header_row(values = c("", "1VS4", "1VS3", "2VS4", "2VS3", "3VS4"), colwidths = c(2, 2, 2, 2, 2, 2)) %>%
    add_header_row(values = c("", "Tests"), colwidths = c(2, 10)) %>%
    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    flextable::compose(i = 3, j = c(3,5,7,9,11), value = as_paragraph("Est. mean"), part = "head") %>% 
    flextable::compose(i = 3, j = c(4,6,8,10,12), value = as_paragraph("p"), part = "head") %>% 
    hline(i = 4, j = c(1:12), part = "body") %>% # To make some horizontal lines
    vline(i = c(1:8), j = c(4,6,8,10), part = "body") %>% # To make some vertical lines
    vline(i = c(2,3), j = c(4,6,8,10), part = "head") 
disc_table

@@

_Table S3.- Number of individuals per treatment that chose the right (R) or left (L) side in each of the numerical tests. p-value indicates the result of the binomial test comparing the number of choices between sides._
```{r, tbl-sides}
#| label: tbl-sides
#| tbl-cap: "Number of individuals per treatment that chose the right (R) or left (L) side in each of the numerical tests. p-value indicates the result of the binomial test comparing the number of choices between sides."
source(here("R", "func.R"))
#
# 1) MAKING THE DF FOR THE TABLE
data_sides <- data_num %>%
  group_by(trt, test_type) %>% # Group by treatment and test
  summarise(
    right_choices = sum(side_choice == "Right", na.rm = TRUE),
    left_choices = sum(side_choice == "Left", na.rm = TRUE),
  ) %>% # Count the number of correct choices
  rowwise() %>%  # Ensure that mutate works row by row
  mutate(
    total_choices = right_choices + left_choices,  # Calculate total choices
    p_value = format_dec(binom.test(right_choices, total_choices)$p.value, 2)  # Perform binom test
  ) %>% # Test for differences between sides
  ungroup() %>%  # Remove rowwise grouping
  mutate(choices_Right_Left_p = paste0("R = ", right_choices, " | L = ", left_choices, " , p = ", p_value), # Create a column with the choices
        trt = recode(trt, 
                 "B_23" = "CORT-Cold (n = 20)", 
                 "A_23" = "Control-Cold (n = 20)", 
                 "B_28" = "CORT-Hot (n = 20)", 
                 "A_28" = "Control-Hot (n = 20)")) %>% # To order the treatments
  dplyr::select(trt, test_type, choices_Right_Left_p) %>% # Remove unused columns
  pivot_wider(names_from = test_type, values_from = c(choices_Right_Left_p)) %>% # To split between tests
data.frame()
#
# 2) MAKING THE TABLE
#
# Split the table_data df by task
sides_table <- flextable(data_sides) %>%
  compose(j = 1, value = as_paragraph(""), part = "header") %>%
  compose(j = 2, value = as_paragraph("1 VS 4"), part = "header") %>%
  compose(j = 3, value = as_paragraph("1 VS 3"), part = "header") %>%
  compose(j = 4, value = as_paragraph("2 VS 4"), part = "header") %>%
  compose(j = 5, value = as_paragraph("2 VS 3"), part = "header") %>%
  compose(j = 6, value = as_paragraph("3 VS 4"), part = "header") %>%
  set_table_properties( width = 0.9, layout = "autofit") %>%
  align(align = "center", part = "all")
sides_table
```

@@

_Table S4. Number of individuals per treatment that chose the cricket oriente horizontally (Horizontal) or vertically (Vertical) in our control tests. p-value indicates the result of the binomial test comparing the number of choices between both choices._
```{r, tbl-orientation}
#| label: tbl-orientation
#| tbl-cap: "Number of individuals per treatment that chose the cricket oriente horizontally (Horizontal) or vertically (Vertical) in our control tests. p-value indicates the result of the binomial test comparing the number of choices between both choices."
source(here("R", "func.R"))
#
# 1) MAKING THE DF FOR THE TABLE
data_or_res <- data_orient %>%
  mutate(choice_or = ifelse(choice_horizontal == 0, "Vertical", "Horizontal")) %>%
  dplyr::select(trt, choice_horizontal, choice_or) %>%
  group_by(trt) %>% # Group by treatment and test
  summarize(
    Horizontal_Count = sum(choice_or == "Horizontal"),
    Vertical_Count = sum(choice_or == "Vertical")
  ) %>% # Count the number of horizontal and vertical choices
  rowwise() %>%  # Ensure that mutate works row by row
  mutate(
    total_choices = Horizontal_Count + Vertical_Count,  # Calculate total choices
    p_value = format_dec(binom.test(Horizontal_Count, total_choices)$p.value, 3)  # Perform binom test
  ) %>% # Test for differences between sides
  ungroup() %>%  # Remove rowwise grouping
  mutate(trt = recode(trt, 
            "B_23" = "CORT-Cold (n = 20)", 
            "A_23" = "Control-Cold (n = 20)", 
            "B_28" = "CORT-Hot (n = 20)", 
            "A_28" = "Control-Hot (n = 20)")) %>% # To order the treatments
  dplyr::select(trt, Horizontal_Count, Vertical_Count, p_value) %>% # Remove unused columns
data.frame()
#
# 2) MAKING THE TABLE
#
# Split the table_data df by task
orient_table <- flextable(data_or_res) %>%
  compose(j = 1, value = as_paragraph(""), part = "header") %>%
  compose(j = 2, value = as_paragraph("Horizontal"), part = "header") %>%
  compose(j = 3, value = as_paragraph("Vertical"), part = "header") %>%
  compose(j = 4, value = as_paragraph("p-value"), part = "header") %>%
  set_table_properties( width = 0.9, layout = "autofit") %>%
  align(align = "center", part = "all")
orient_table
```
